---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
## Another Multiple Linear Regression Example

Another example using the Credit dataset.  

Libraries  
```{r}
library(tidyverse)
library(GGally) #for ggpairs function
library(MASS) #access to forward and backward selection algorithms
library(leaps) #best subset selection
```

Read-in dataset  
```{r}
credit = read_csv("CreditData.csv")
```

Get rid of missing data rows  
```{r}
credit = credit %>% drop_na() #delete any row with an NA value
str(credit) #check structure after the drop
```

Our Y (response) variable in this dataset is "AnnualCharges".  Let's look at ggpairs plot for visualization and correlation.  
```{r}
ggpairs(credit)
```

Model with best single variable (by correlation).  
```{r}
mod1 = lm(AnnualCharges ~ AnnualIncome, credit) #create linear regression model
summary(mod1) #examine the model
```
Adjusted R-squared value of this univariate model is: 0.3152. Can we improve upon this by adding additional variables?  

Start by building two models: One model that contains all of the predictors and one that is empty.
```{R}
allmod = lm(AnnualCharges ~., credit) #use the ~. to include all predictors rather than typing them all in
summary(allmod)

emptymod = lm(AnnualCharges ~1, credit) #use ~1 to build an empty model
summary(emptymod)
```
Backward stepwise regression
```{r}
#backward
backmod = stepAIC(allmod, direction = "backward", trace = TRUE) 
#trace = TRUE shows how the model is built (which variables are removed)
summary(backmod)
```
Backward does not strip any variables out.  

Forward stepwise regression
```{r}
#forward
forwardmod = stepAIC(emptymod, direction = "forward", scope=list(upper=allmod,lower=emptymod),
                      trace = TRUE) #trace = TRUE shows how the model is built (which variables are added)
summary(forwardmod) #note multicollinearity with FullBath with a negative coefficient
```
Forward yields same model.  



