## Classification Tree Example

Libraries  
```{r}
library(tidyverse)
library(caret) #for splitting functions
library(rpart) #for classification trees
library(RColorBrewer) #better visualization of classification trees
library(rattle) #better visualization of classification trees
```

Load data    
```{r}
admit = read_csv("Admission.csv")
```

Structure and summary
```{R}
str(admit)
summary(admit)
```

Factor conversion. Convert the response variable SeriousDlqin2yrs.
```{r}
admit = admit %>% mutate(Admission_YN = as.factor(Admission_YN)) %>% 
  mutate(Admission_YN = fct_recode(Admission_YN, "No" = "0", "Yes" = "1" )) 

str(admit)
```

Now we'll split the data.  
```{r}
set.seed(123) 
train.rows = createDataPartition(y = admit$Admission_YN, p=0.7, list = FALSE) #70% in training
train = admit[train.rows,] 
test = admit[-train.rows,]
```

Let's build a classification tree.  
```{r}
tree1 = rpart(Admission_YN  ~., train, method="class")
fancyRpartPlot(tree1)
```

```{r}
printcp(tree1)
plotcp(tree1)
```
Prune the tree (at minimum cross-validated error)  
```{r}
tree2 = prune(tree1,cp= tree1$cptable[which.min(tree1$cptable[,"xerror"]),"CP"])
#most of the code in the line above can be left untouched. Just change tree1 to the name of your tree model (if it's not called tree1)
fancyRpartPlot(tree2)
```


Predictions on training set  
```{r}
treepred = predict(tree2, train, type = "class")
head(treepred)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred,train$Admission_YN,positive="Yes") #predictions first then actual
```

Predictions on testing set  
```{r}
treepred_test = predict(tree2, newdata=test, type = "class")
head(treepred_test)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred_test,test$Admission_YN,positive="Yes") #predictions first then actual
```




