## Classification Tree (Another example)

Libraries  
```{r}
library(tidyverse)
library(caret) #for splitting functions
library(rpart) #for classification trees
library(RColorBrewer) #better visualization of classification trees
library(rattle) #better visualization of classification trees
```

Load data from the CSData.csv file.  
```{r}
credit = read_csv("CSData.csv")
```

Structure and summary
```{R}
str(credit)
summary(credit)
```

Factor conversion. Convert the response variable SeriousDlqin2yrs.
```{r}
credit = credit %>% mutate(SeriousDlqin2yrs = as.factor(SeriousDlqin2yrs)) %>% 
  mutate(SeriousDlqin2yrs = fct_recode(SeriousDlqin2yrs, "No" = "0", "Yes" = "1" )) 

str(credit)
```

Data cleaning (same as done in earlier lectures).  
```{r}
credit = credit %>% filter(RevolvingUtilizationOfUnsecuredLines < 2)
credit = credit %>% filter(DebtRatio < 5)
credit = credit %>% filter(MonthlyIncome < 20000) %>% drop_na()
credit = credit %>% filter(NumberOfOpenCreditLinesAndLoans < 40)
credit = credit %>% filter(NumberOfTimes90DaysLate < 10)
credit = credit %>% filter(NumberRealEstateLoansOrLines < 10)
credit = credit %>% filter(NumberOfDependents < 10)
```

Now we'll split the data.  
```{r}
set.seed(123) 
train.rows = createDataPartition(y = credit$SeriousDlqin2yrs, p=0.7, list = FALSE) #70% in training
train = credit[train.rows,] 
test = credit[-train.rows,]
```

Let's build a classification tree.  
```{r}
tree1 = rpart(SeriousDlqin2yrs  ~., train, method="class")
fancyRpartPlot(tree1)
```

```{r}
printcp(tree1)
plotcp(tree1)
```

Predictions on training set  
```{r}
treepred = predict(tree1, train, type = "class")
head(treepred)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred,train$SeriousDlqin2yrs,positive="Yes") #predictions first then actual
```

Predictions on testing set  
```{r}
treepred_test = predict(tree1, test, type = "class")
head(treepred_test)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred_test,test$SeriousDlqin2yrs,positive="Yes") #predictions first then actual
```




