## Making Predictions with Simple Linear Regression Model

Needed libraries  
```{r}
library(tidyverse)
```

Read-in the data. Before doing this make sure that you have placed the CreditData.csv file (downloadable from Canvas) in your project's working directory.  

```{r}
credit = read_csv("CreditData.csv")
```

Get rid of missing data rows  
```{r}
credit = credit %>% drop_na() #delete any row with an NA value
```

Build a regression model with AnnualIncome to predict AnnualCharges.  
```{r}
mod1 = lm(AnnualCharges ~ AnnualIncome, credit) #create linear regression model
summary(mod1) #examine the model
```

Prediction for AnnualIncomes of 75 and 100?  
```{r}
#Manually
3146.361 + 121.355*75
3146.361 + 121.355*100

#Using predict function
testdata = data.frame(AnnualIncome = c(75,100))
predict(mod1, newdata = testdata, interval = "predict")
```

```{r}
#Prediction intervals
temp_var = predict(mod1, interval = "prediction")
new_df = cbind(credit, temp_var)

ggplot(new_df, aes(x = AnnualIncome, y = AnnualCharges)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_line(aes(y=lwr), color = "red", linetype = "dashed") +
  geom_line(aes(y=upr), color = "red", linetype = "dashed") +
  theme_bw() 
```
