---
title: "Module 4 Trees Assignment"
author: "Austin Lankford"
date: "2/17/2020"
output: word_document
---


```{r}
library(tidyverse)
library(caret)
library(rpart)
library(rattle)
library(RColorBrewer)
```



```{r}
parole <- read.csv("parole.csv")
summary(parole)
```


```{r}
parole = parole %>% mutate(male = as_factor(as.character(male))) %>%
mutate(male = fct_recode(male,
"female" = "0",
"male" = "1"))

parole = parole %>% mutate(state = as_factor(as.character(state))) %>%
mutate(state = fct_recode(state,
"Other" = "1",
"Kentucky" = "2",
"Louisiana" = "3",
"Virginia" = "4"))

parole = parole %>% mutate(race = as_factor(as.character(race))) %>%
mutate(race = fct_recode(race,
"not_white" = "2",
"white" = "1"))

parole = parole %>% mutate(violator = as_factor(as.character(violator))) %>%
mutate(violator = fct_recode(violator,
"no" = "0",
"yes" = "1"))

parole = parole %>% mutate(crime = as_factor(as.character(crime))) %>%
mutate(crime = fct_recode(crime,
"Other" = "1",
"larceny" = "2",
"drugs" = "3",
"driving" = "4"))

parole = parole %>% mutate(multiple.offenses = as_factor(as.character(multiple.offenses))) %>%
mutate(multiple.offenses = fct_recode(multiple.offenses,
"no" = "0",
"yes" = "1"))


```



# Task 1: Split the data into training and testing sets. Your training set should have 70% of the data. Use a random number (set.seed) of 12345.

```{r}
set.seed(12345) 
train.rows = createDataPartition(y = parole$violator, p=0.7, list = FALSE)
train = parole[train.rows,] 
test = parole[-train.rows,]
```


# Task 2: Create a classification tree using all of the predictor variables to predict “violator” in the training set. Plot the tree.

#Task 3: For the tree created in Task 2, how would you classify a 40 year-old parolee from Louisiana whoserved a 5 year prison sentence? Describe how you “walk through” the classification tree to arrive at your answer.

### 1) State = Louisiana -> step right. Race - if white, step right, is other, step left. If not white, since age > 30, parolee is classified as "no". If white, since time served is >3.9 years, parolee is classified as "yes".

```{r}
tree1 = rpart(violator ~., train, method="class")
fancyRpartPlot(tree1)
```

```{r}
printcp(tree1)
plotcp(tree1)
```


# Task 4: Use the printcp function to evaluate tree performance as a function of the complexity parameter (cp). What cp value should be selected? Note that the printcp table tends to be a more reliable tool than theplot of cp.

### CP Value os 0.0303 has been selected as the cross validation error increases with higher complexity. Increasing our complexity would risk overfitting.

```{r}
tree2 = rpart(violator ~., train, cp=.03, method="class")
fancyRpartPlot(tree2)
```


```{r}
printcp(tree2)
plotcp(tree2)
```


# Task 5: Prune the tree from Task 2 back to the cp value that you selected in Task 4. Do not attempt to plot the tree. You will find that the resulting tree is known as a “root”. A tree that takes the form of a root is essentially a naive model that assumes that the prediction for all observations is the majority class.
# Which class (category) in the training set is the majority class (i.e., has the most observations)?

```{r}
tree3 = prune(tree1,cp= .03)
fancyRpartPlot(tree3)

```


# Task 6: Use the unpruned tree from Task 2 to develop predictions for the training data. Use caret’s confusionMatrix function to calculate the accuracy, specificity, and sensitivty of this tree on the training data. Note that we would not, in practice, use an unpruned tree as such a tree is very likely to overfit on new data.

### I'm recieving the error "Error in `[.default`(data, , positive) : subscript out of bounds" when I run the Confusion Matrix code. I'm not sure why.

```{r}
treepred = predict(tree1, train, type = "class")
head(treepred)
```

```{r}
#confusionMatrix(treepred,train$violator, positive="Yes")
```


# Task 7: Use the unpruned tree from Task 2 to develop predictions for the testing data. Use caret’s confusionMatrix function to calculate the accuracy, specificity, and sensitivty of this tree on the testing data.
# Comment on the quality of the model.

```{r}
treepred2 = predict(tree3, train, type = "class")
head(treepred2)
```

### Same error for the below

```{r}
#confusionMatrix(treepred2,train$violator, positive="Yes")
```


#Task 8: Read in the “Blood.csv” dataset. The dataset contains five variables:
## Mnths_Since_Last: Months since last donation
## TotalDonations: Total number of donation
## Total_Donated: Total amount of blood donated
## Mnths_Since_First: Months since first donation
## DonatedMarch: Binary variable representing whether he/she donated blood in March (1 = Yes, 0 = No)

# Convert the DonatedMarch variable to a factor and recode the variable so 0 = “No” and 1 = “Yes”.

```{r}
Blood = read.csv("Blood.csv")

```

```{r}
Blood = Blood %>% mutate(DonatedMarch = as_factor(as.character(DonatedMarch))) %>%
mutate(DonatedMarch = fct_recode(DonatedMarch,
"No" = "0",
"Yes" = "1"))
```


#Task 9: Split the dataset into training (70%) and testing (30%) sets. You may wish to name your training and testing sets “train2” and “test2” so as to not confuse them with the parole datsets
# Use set.seed of 1234. Then develop a classification tree on the training set to predict “DonatedMarch”.

```{r}
set.seed(1234) 
train.rows2 = createDataPartition(y = Blood$DonatedMarch, p=0.7, list = FALSE)
train2 = Blood[train.rows2,] 
test2 = Blood[-train.rows2,]

```


#Evaluate the complexity parameter (cp) selection for this model.

### Optimal cp is 0.026

```{r}
tree1_Blood = rpart(DonatedMarch ~., train2, method="class")
fancyRpartPlot(tree1_Blood)
```


```{r}
printcp(tree1_Blood)
plotcp(tree1_Blood)
```


#Task 10: Prune the tree back to the optimal cp value, make predictions, and use the confusionMatrix function on the both training and testing sets. Comment on the quality of the predictions.

```{r}
tree2_Blood = prune(tree1_Blood,cp= .026)
fancyRpartPlot(tree2_Blood)

```



```{r}
treepred_Blood = predict(tree2_Blood, train2, type = "class")
head(treepred_Blood)
```

### Accuracy .82
### Sensitivity .30
### Specificity .97

```{r}
confusionMatrix(treepred_Blood,train2$DonatedMarch, positive="Yes")
```



