---
title: "Module 4 Assignment 1"
author: "Austin Lankford"
date: "2/17/2020"
output: word_document
---

```{r}
library(tidyverse)
library(VIM)
library(mice)
library(naniar)
```

```{r}
grades <- read.csv("class-grades.csv")
```




# Task 1: How much data is missing and in what variables?

### Missingness: "Tutorial" - 1, "Midterm" - 3, "TakeHome" - 4, "Final" - 4

```{r}
summary(grades)
str(grades)
glimpse(grades)
```


# Task 2: Use the VIM package to visualize missingness. Does there appear to be systematic missingness? In other words, are there students that are mising multiple pieces of data?

### There are more "7" and "8" students with missing data than others. Students with the prefix "6", "7", and "8" are the only students with missing data.

```{r}
aggr(grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
```


```{r}
gg_miss_var(grades)
```

```{r}
barMiss(grades, only.miss = FALSE)
```


# Task 3: Use row-wise deletion of missing values to create a new data frame. How many rows remain in this data frame?

### 89 rows remain in the data set

```{r}
rowise_drop_na_grades = grades %>% drop_na()
summary(grades)

```

#Task 4: Use column-wise deletion of missing values to create a new data frame (from the original data frame not from the data frame created in Task 3). How many columns remain in this data frame?

### 2 Columns remain

```{r}
column_wise_drop_na_grades = grades %>% select(-Final, -TakeHome, -Midterm, -Tutorial) 
```

# Task 5: Which approach (Task 3 or Task 4) seems preferable for this dataset? Briefly discuss your answer.

### Rowwise deletion is prefereable in this case. There really isn't much data that's missing. Columnwise deletion leavues us with only two variables.


# Task 6 Use the code below to impute the missing values in the dataset using the mice package

# Task 7: Briefly discuss potential issues that could be encountered when working with missing data. Describe situations where imputation may not be advisable.

### Missing data is very common and there are mutliple ways to appraoch it. In an ideal situation either you missing data is in a colu,mn associated with a variable you don't need anyways and columnwise deletion would be best fit. In the event that you have a few items of missing data, rowise is acceptable as long as it doesn't remove a significant portion of your data. Imputation is a viable appraoch but it is based on predictive means modeling. If there are only a few missing data points, and those data points happen to have other atrributable factors that would cause the observation to be considered an outlier it could alter your modeling accuracy. Each situation is different and much be approached with caution. There are also regressive means to impute the data such that you can apply a predictive model to determine what the na's would actually be in reality, but as with all other means to handle missingness, this comes with it's own risks.

```{r}
grades_imp = mice(grades, m=1, method = "pmm", seed = 12345)
#in line above: m=1 -> runs one imputation, seed sets the random number seed to get repeatable results
summary(grades_imp)
densityplot(grades_imp)
#red imputed, blue original, only shows density plots when more than 1 value the variable was imputed
#note that the density plots are fairly uninteresting given the small amount of missing data
grades_complete = complete(grades_imp)
summary(grades_complete)
```

