---
title: "Module 2 Linear Regression"
author: "Austin Lankford"
date: "2/3/2020"
output: word_document
---

```{r}
air = airquality
```

```{r}
#install.packages("car")
#install.packages("lmtest")
library(car)
library(lmtest)
library(tidyverse)
library(GGally)
library(naniar)
```

# Dataset Exploration
## There are 7 NA's from Solar.R, 37 NA's from Ozone but the rest of the data seems to be intact. In total there are 153 observations and 6 total variables. 

```{r}
summary(air)
str(air)
glimpse(air)
```


```{r}
gg_miss_var(air)
```

# Deletion of NA's
## After deleting the NA's, there are 111 observations for the remaining 6 variables.
```{r}
air = air %>%
  drop_na()
```

```{r}
summary(air)
str(air)
gg_miss_var(air)
```

# Correlation
## In reference to the Ozone field, the strongest correlation is with Temp and wind, the weakest correlation is with Day.

```{r}
ggpairs(air, label = TRUE)
```

```{r}
ggcorr(air)
```

# Data Visualization
## There is a positive linear relationship between Temp and Ozone as demonstrated in the scatterplot below.

```{r}
ggplot(air) +
 aes(x = Temp, y = Ozone) +
 geom_point(size = 1L, colour = "#0c4c8a") +
 theme_minimal()
```

# Simple Linear Regression
## The simple linear regression with Temp predicting Ozone produces a p value that is statistically significant and an R squared that accounts for roughly 48% of the variance. The adjusted R Squared does not change much from the regular R Squared so I would say this is a reliable statistic.

```{r}
regression = lm(Ozone ~ Temp, air) 
summary(regression) 

```

```{r}
ggplot(air) +
 aes(x = Temp, y = Ozone) +
 geom_point(size = 1L, colour = "#0c4c8a") + geom_smooth()
 theme_minimal()
```

```{r}
testdata = data.frame(Temp = c(80))
predict(regression, newdata = testdata, interval = "predict")
```

# Testing Model
## The model is useful to some extent as a predictive model but can be made better by adding more variables, although not all variables are significant and should be excluded.
```{r}
emptymod = lm(Ozone ~1, air)
summary(emptymod)

allmod = lm(Ozone ~ Temp + Solar.R + Wind + Day + Month, air, ) 
summary(allmod)
```

```{r}

```





