---
title: "Module 2 Assignment 2 Multiple Linear Regression"
author: "Austin Lankford"
date: "2/3/2020"
output: word_document
---

```{r}
library(tidyverse)
library(GGally)
library(MASS)
library(car)
library(gridExtra)
```

```{r}
library(readr)
hour <- read_csv("hour.csv")
View(hour)
```

# Why we convert the variables to factors
## These variables are converted to factors so that they may be viewed as a specific input. Such that all instances of X occurred in factor A, B, C, 1, 2, 3, etc. So that things like traffic times can be viewed as proportionality weighted during times like rush hour.

```{r}
hour = hour %>% mutate(season = as_factor(as.character(season))) %>%
mutate(season = fct_recode(season,
"Spring" = "1",
"Summer" = "2",
"Fall" = "3",
"Winter" = "4"))

```

```{r}
hour = hour %>% mutate(yr = as_factor(as.character(yr)))
hour = hour %>% mutate(mnth = as_factor(as.character(mnth)))
hour = hour %>% mutate(hr = as_factor(as.character(hr)))
```

```{r}
hour = hour %>% mutate(holiday = as_factor(as.character(holiday))) %>%
mutate(holiday = fct_recode(holiday,
"NotHoliday" = "0",
"Holiday" = "1"))
```

```{r}
hour = hour %>% mutate(workingday = as_factor(as.character(workingday))) %>%
mutate(workingday = fct_recode(workingday,
"NotWorkingday" = "0",
"Workingday" = "1"))
```

```{r}
hour = hour %>% mutate(weathersit = as_factor(as.character(weathersit))) %>%
mutate(weathersit = fct_recode(weathersit,
"NoPrecip" = "1",
"Misty" = "2",
"LightPrecip" = "3",
"HeavyPrecip" = "4"))
```

```{r}
glimpse(hour)
```

# Hum, atemp, temp, and nstant are most correlated with count.

```{r}
ggcorr(hour)
```


```{r}


```

```{r}
ggplot(hour) +
 aes(x = mnth, y = count) +
 geom_boxplot(adjust = 5L, scale = "area", fill = "#0c4c8a") +
 theme_minimal()
```

```{r}
ggplot(hour) +
 aes(x = hr, y = count) +
 geom_boxplot(adjust = 5L, scale = "area", fill = "#0c4c8a") +
 theme_minimal()
```

```{r}
ggplot(hour) +
 aes(x = weathersit, y = count) +
 geom_boxplot(adjust = 5L, scale = "area", fill = "#0c4c8a") +
 theme_minimal()
```

```{r}
ggplot(hour) +
 aes(x = season, y = count) +
 geom_boxplot(adjust = 5L, scale = "area", fill = "#0c4c8a") +
 theme_minimal()
```

# It would stand to reason that the count of rentals would be higher during normal day hours and during nicer weather given the desireable conditions for riding bikes.

```{r}
emptymod = lm(count ~1, hour) 
summary(emptymod)

```
```{r}
allmod = lm(count ~ instant + dteday + season + yr + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed + casual + registered, hour,) 
summary(allmod) 

```

```{r}
forwardmod = stepAIC(emptymod, direction = "forward", scope=list(upper=allmod,lower=emptymod), trace = TRUE)
```

```{r}
hour2 = hour %>% dplyr::select(-c(instant, dteday, registered, casual))
```

```{r}
emptymod2 = lm(count ~1, hour) 
summary(emptymod2)

allmod2 = lm(count ~ + season + yr + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed, hour,) 
summary(allmod2) 
```

## In the forwardwise step model, the variables selected are Step:  AIC=160711.7count ~ hr + atemp + yr + weathersit + season + mnth + hum + weekday + holiday + windspeed + temp + workingday

```{r}
forwardmod2 = stepAIC(emptymod2, direction = "forward", scope=list(upper=allmod2,lower=emptymod2), trace = TRUE)
```

## The variables selected by the backmod are Start:  AIC=160711.7 count ~ +season + yr + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed

```{r}
backmod2 = stepAIC(allmod2, direction = "backward", trace = TRUE) 
```

```{r}
summary(forwardmod2)
summary(backmod2)
```

## The forward and back stepwise model tests have resulted in the same variable combination with the same adjusted R Squared. 

## WorkingDay is likely being kicked out because the weekday variable represents the weekend and the holiday variable represents the holidays so working day is a redundant consideration.
