## Random Forests

```{r}
options(tidyverse.quiet = TRUE)
library(titanic)
library(tidyverse)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(ranger) #for random forests
library(caret)
```

Read in dataset   
```{r}
titanic = titanic::titanic_train
```

Structure and summary
```{r}
str(titanic)
summary(titanic)
```

Factor conversion and recoding  
```{r}
titanic = titanic %>% mutate(Survived = as.factor(Survived)) %>% 
  mutate(Survived = fct_recode(Survived, "No" = "0", "Yes" = "1" )) %>%
  mutate(Pclass = as.factor(Pclass)) %>% mutate(Sex = as.factor(Sex)) %>%
  mutate(Embarked = as.factor(Embarked)) %>% 
  mutate(Embarked = fct_recode(Embarked,"Unknown"="","Cherbourg"="C","Southampton"="S","Queenstown"="Q"))

titanic$Cabin[titanic$Cabin==""] = NA #convert blanks in cabin to NA

str(titanic)
```

Column-wise deletion of the "Cabin" variable.  
```{r}
titanic = titanic %>% select(-Cabin) 
vim_plot = aggr(titanic, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
```

```{r}
#select only variables relevant to our analysis
titanic = titanic %>% select(c("Survived","Pclass","Sex","Age","SibSp","Parch","Embarked"))

imp_age = mice(titanic, m=1, method='pmm', printFlag=FALSE)
summary(imp_age)
```

Merge the imputed values into our titanic data frame  
```{r}
titanic_complete = complete(imp_age) 
summary(titanic_complete)
```

###Building Random Forest Model with Caret
Note use of non-formula interface due to caret and ranger's handling of factors. The non-formula interface leaves the categorical variables as factors (usually desirable) while the formula interface converts to dummy variables.

Random forest
```{r}
fit_control = trainControl(method = "cv",  
                           number = 10) #set up 10 fold cross-validation

#rf_fit = train(Survived ~.,

set.seed(123)  
rf_fit = train(x=titanic_complete[,-1], y=titanic_complete$Survived,
                 method = "ranger", 
                 importance = "permutation",
                 trControl = fit_control)
#notice exclusion of "data = " line in block of code above. Not needed as data is explicitly indicated via non-formula interface
```

Check out random forest details  
```{r}
varImp(rf_fit)
rf_fit
```

Predictions  
```{r}
predRF = predict.train(rf_fit, titanic_complete)
head(predRF)
```

Confusion matrix
```{r}
confusionMatrix(predRF, titanic_complete$Survived, positive = "Yes")
```







