## Another Random Forest

```{r}
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(ranger) #for random forests
library(caret)
```

Load data from the CSData.csv file.  
```{r}
credit = read_csv("CSData.csv")
```

Structure and summary
```{R}
str(credit)
summary(credit)
```

Factor conversion. Convert the response variable SeriousDlqin2yrs.
```{r}
credit = credit %>% mutate(SeriousDlqin2yrs = as.factor(SeriousDlqin2yrs)) %>% 
  mutate(SeriousDlqin2yrs = fct_recode(SeriousDlqin2yrs, "No" = "0", "Yes" = "1" )) 

str(credit)
```

Data cleaning (same as done in earlier).  
```{r}
credit = credit %>% filter(RevolvingUtilizationOfUnsecuredLines < 2)
credit = credit %>% filter(DebtRatio < 5)
credit = credit %>% filter(MonthlyIncome < 20000) %>% drop_na()
credit = credit %>% filter(NumberOfOpenCreditLinesAndLoans < 40)
credit = credit %>% filter(NumberOfTimes90DaysLate < 10)
credit = credit %>% filter(NumberRealEstateLoansOrLines < 10)
credit = credit %>% filter(NumberOfDependents < 10)
```

Now we'll split the data.  
```{r}
set.seed(123) 
train.rows = createDataPartition(y = credit$SeriousDlqin2yrs, p=0.7, list = FALSE) #70% in training
train = credit[train.rows,] 
test = credit[-train.rows,]
```

Random forest with caret
```{r}
fit_control = trainControl(method = "cv",
                           number = 10) #set up 10 fold cross-validation

set.seed(123)
rf_fit = train(x=as.matrix(train[,-1]), y=as.matrix(train$SeriousDlqin2yrs),    
                method = "ranger",  
                importance = "permutation",
                trControl = fit_control)
#note the as.matrix command. Passing a tibble to ranger can result in warnings.
```

Save the model to a file to load later (if needed)  
```{r}
# saveRDS(rf_fit, "rf_fit.rds")
```

Load the model  
```{r}
# rf_fit = readRDS("rf_fit.rds")
```

Check out random forest details  
```{r}
varImp(rf_fit)
rf_fit
```

Predictions  
```{r}
predRF = predict(rf_fit)
head(predRF)
```

Confusion matrix
```{r}
confusionMatrix(predRF, train$SeriousDlqin2yrs, positive = "Yes")
```

Predictions on test
```{r}
predRF_test = predict(rf_fit, newdata = test)
```

Confusion matrix
```{r}
confusionMatrix(predRF_test, test$SeriousDlqin2yrs, positive = "Yes")
```






