## Regression Trees

Libraries  
```{r}
library(tidyverse)
library(caret) 
library(rpart)
library(rattle)
library(RColorBrewer)
```

Read-in dataset  
```{r}
credit = read_csv("CreditData.csv")
```

Get rid of missing data rows (**any data cleaning/prepartion should take place before splitting**).  
```{r}
credit = credit %>% drop_na() #delete any row with an NA value
str(credit) #check structure after the drop
```

Split the data (training and testing)  
```{r}
set.seed(123)
train.rows = createDataPartition(y = credit$AnnualCharges, p=0.7, list = FALSE) #70% in training
train = credit[train.rows,] 
test = credit[-train.rows,]
```

Create regression tree  
```{r}
regtree1 = rpart(AnnualCharges~., method="anova", train)
fancyRpartPlot(regtree1)
printcp(regtree1)  
plotcp(regtree1) 
```
Develop predictions on the training set
```{r}
train_preds = predict(regtree1)
head(train_preds) #see first six predictions
```

Now we can manually calculate the R squared value on train
```{r}
SSE = sum((train$AnnualCharges - train_preds)^2) #sum of squared residuals from model
SST = sum((train$AnnualCharges - mean(train$AnnualCharges))^2) #sum of squared residuals from a "naive" model
1 - SSE/SST #definition of R squared
```

Develop predictions on the testing set
```{r}
test_preds = predict(regtree1, newdata = test)
```

Now we can manually calculate the R squared value on test
```{r}
SSE = sum((test$AnnualCharges - test_preds)^2) #sum of squared residuals from model
SST = sum((test$AnnualCharges - mean(test$AnnualCharges))^2) #sum of squared residuals from a "naive" model
1 - SSE/SST #definition of R squared
```



